---
title: "Sentiment Application"
author:  "Chris Bailey"
date: '`r Sys.Date()`'
output: 
  flexdashboard::flex_dashboard:
    theme: cosmo
    orientation: rows
    vertical_layout: fill
runtime: shiny
resource:
  - consolidatedBrandFile.csv
  - loughran.csv
  - afinn_111.xlsx
---

```{r, include=FALSE}
library(flexdashboard)
library(shiny)
library(shinythemes)
library(openintro)
library(highcharter)
library(knitr)
library(lubridate) 
library(scales) 
library(tidytext) 
library(tidyverse)
library(broom) 
library(textdata)
library(plotly)
library(wordcloud)
library(RColorBrewer)
library(reshape2) 
library(ggraph)
library(igraph)
library(plotly)
library(gtrendsR)
library(reshape2)
library(ggrepel)
library(grid)
library(crosstalk)


theme_set(theme_light())
mycolors <- c("blue", "#FFC125", "darkgreen", "darkorange")
```

```{r, include=FALSE }
review <- readr::read_csv('raw_text_consolidated.csv') %>%
  mutate(week = as.Date(floor_date(created_at, "week", week_start = 1)))
review$created_at <- as.Date(review$created_at)
loughran_data <- readr::read_csv('loughran.csv')
afinn_111 <- readxl::read_xlsx('afinn_111.xlsx')
# C:\\Users\\cbail\\Desktop\\DataFiles\\patriot_sent\\SentimentApplication\\
```

```{r, include=FALSE}
review_copy <- review %>% 
  filter(brand %in% c("ATT","CenturyLink","Spectrum","Wave","Xfinity")) 

review_copy$review <-  gsub("https\\S*", "", review_copy$review)
review_copy$review <-  gsub("@\\S*", "", review_copy$review)
review_copy$review <-  gsub("amp", "", review_copy$review)
review_copy$review <-  gsub("[\r\n]", "", review_copy$review)
review_copy$review <-  gsub("[[:punct:]]", "", review_copy$review)
replace_reg1 <- "https://t.co/[A-Za-z\\d]+|" 
replace_reg2 <- "http://[A-Za-z\\d]+|&amp;|&lt;|&gt;|RT|https+|" 
replace_reg <- paste0(replace_reg1, replace_reg2) 
unnest_reg <- "([^A-Za-z_\\d#@']|'(?![A-Za-z_\\d#@]))"
remove_words <- c("hey")

tidy_tweets <- review_copy %>%
  # filter(!str_detect(text, "^RT")) %>%
  mutate(text = str_replace_all(review, replace_reg, "")) %>% 
  # unnest_tokens(word, text, token = "tweets", strip_punct =TRUE) %>%
  unnest_tokens(word, review, token = "regex", pattern = unnest_reg) %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         !word %in% remove_words,
         str_detect(word, "[a-z]"))

sd <- SharedData$new(tidy_tweets)
```

Sidebar {.sidebar}
===================================================

### <font size="5">**Filters**</font>

```{r}
    f1 <- filter_select("brand", "Select Brand:", sd, ~brand, allLevels = FALSE)
    # c3 <- filter_checkbox("segment", "Select Customer Segment:", sd_2, ~customer_segment, columns = 2, allLevels = FALSE)
    # c4 <- filter_checkbox("waveg", "Select WaveG:", sd_2, ~wave_g, columns = 2, allLevels = FALSE)

# filter_1 <- bscols(widths = c(NA,NA,NA),
#        device = c("lg"),
#   list(c2,c3,c4)
#   )

filter_1 <- bscols(
  list(f1)
  )

filter_1
```

Data {data-icon="fa-database"}
==================================================

Row
--------------------------------------------------

### <font size="5">**Social Media Reviews by Brand**</font>
```{r}
p1 <- review_copy %>%
  group_by(brand) %>%
  summarise(units = n()) %>%
  plot_ly(labels = ~brand,
          values = ~units,
          marker = list(colors = mycolors)) %>%
  add_pie(hole = 0.4) %>%
  layout(xaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F),
         yaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F))
p1
```

### <font size="5">**Social Media Reviews by Week**</font>
```{r}
review_ts_chart <- review_copy %>%
  select(created_at, review, week, brand, region, src) %>%
  arrange(desc(as.Date(created_at)))

review_ts_chart %>%
  arrange(desc(as.Date(created_at))) %>%
  select(review, created_at, brand) %>%
  group_by(created_at, brand) %>%
  summarize(count = n()) %>%
  ggplot(aes(created_at, count, brand, fill = factor(brand), color=brand)) +
  geom_line(size = 1) +
  facet_wrap(~ brand, scales = "free") +
  expand_limits(y=0) +
  #scale_y_continuous(limits = c(0,100)) +
  labs(title = "Count of Reviews by Week and Brand", 
          y = "Review count",
          x = "Week",
       subtitle = "Includes reviews sourced from Yelp, FaceBook, and Twitter") +
  theme(strip.background = element_rect(fill = "blue"), 
        strip.text = element_text(size = 12, face = "bold"),
        legend.position = "none",
        plot.title.position = "plot")
```

Row
--------------------------------------------------

### <font size="5">**Social Media Reviews by Region**</font>
```{r}
p1 <- review_copy %>%
  group_by(region) %>%
  summarise(units = n()) %>%
  plot_ly(labels = ~region,
          values = ~units,
          marker = list(colors = mycolors)) %>%
  add_pie(hole = 0.4) %>%
  layout(xaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F),
         yaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F))
p1
```

### <font size="5">**Social Media Reviews by Week**</font>
```{r}
review_ts_chart <- review_copy %>%
  select(created_at, review, week, brand, region, src) %>%
  arrange(desc(as.Date(created_at)))

review_ts_chart %>%
  arrange(desc(as.Date(created_at))) %>%
  select(review, created_at, region) %>%
  group_by(created_at, region) %>%
  summarize(count = n()) %>%
  ggplot(aes(created_at, count, region, fill = factor(region), color=region)) +
  geom_line(size = 1) +
  facet_wrap(~ region, scales = "free") +
  expand_limits(y=0) +
  #scale_y_continuous(limits = c(0,100)) +
  labs(title = "Count of Reviews by Week and Brand", 
          y = "Review count",
          x = "Week",
       subtitle = "Includes reviews sourced from Yelp, FaceBook, and Twitter") +
  theme(strip.background = element_rect(fill = "blue"), 
        strip.text = element_text(size = 12, face = "bold"),
        legend.position = "none",
        plot.title.position = "plot")
```

Topics {data-icon="fa-bullhorn"}
==================================================

Row
--------------------------------------------------

### <font size="5">**Wave Broadband Key Topic Analysis**</font>
```{r}
renderPlot({
wave_top_word <- sd$data(withSelection = TRUE, withFilter = TRUE) %>%
    count(word, week) %>%
  bind_tf_idf(word, week, n) %>%
  arrange(desc(tf_idf)) %>%
  group_by(week) %>%
  #top_n(1, tf_idf) %>% 
  distinct(week, .keep_all = TRUE) %>%
  arrange(week) 

# wave_top_word <- tidy_tweets %>%
#   filter(brand == "Wave") %>%
#   # filter(date>= "2020-01-01") %>%
#   count(word, week) %>%
#   bind_tf_idf(word, week, n) %>%
#   arrange(desc(tf_idf)) %>%
#   group_by(week) %>%
#   #top_n(1, tf_idf) %>% 
#   distinct(week, .keep_all = TRUE) %>%
#   arrange(week)

wave_top_word %>%
  ggplot(aes(week, n, label= word, color=word)) +
  geom_line(color = "royalblue", size = 2) +
  geom_point(color = "royalblue", size = 5) +
  # geom_text_repel(aes(label = word, color = word)) +
  geom_label_repel(size = 8,
                   box.padding = unit(0.5, "lines")) +
  expand_limits(y = 0) +
  labs(title = "Most common words by week: Wave", 
          y = "Word count",
          x = "Word") +
  theme(legend.position = "none",
        plot.title=element_text(size=16,face="bold"),
        # axis.text=element_text(size=16),
        axis.title=element_text(size=18,face="bold"),
        axis.text.x = element_text(size = 18),
        axis.text.y = element_text(size = 18)
        )
})
```

Word Trends {data-icon="fa-chart-line"}
==================================================
  
Row
--------------------------------------------------
  
### <font size="5">**Wave Broadband Key Trending Topics**</font>
```{r}
# rolling_dt <- today() - months(3) #lubridate

words_by_time <- tidy_tweets %>%
  filter(brand=="Wave") %>%
  # filter(!str_detect(word, "^@")) %>%
  # filter(date> "2020-01-01") %>%
  mutate(time_floor = floor_date(created_at, unit = "week")) %>% 
  count(time_floor, word) %>% 
  # count(time_floor, period, word) %>% 
  ungroup() %>% 
  group_by(time_floor) %>%
  # group_by(period, time_floor) %>% 
  mutate(time_total = sum(n)) %>% 
  group_by(word) %>% 
  mutate(word_total = sum(n)) %>% 
  ungroup() %>% 
  rename(count = n) %>% 
  filter(word_total>10)  # nbr of words used at least x times

nested_data <- words_by_time %>%
  # nest(-word,-time_floor)
  nest_legacy(-word)

nested_models <- nested_data %>%
  mutate(models = map(data, ~glm(cbind(count, time_total) ~ time_floor, ., family = "binomial")))

slopes <- nested_models %>%
  unnest_legacy(map(models, tidy)) %>%
  filter(term == "time_floor") %>%
  mutate(adjusted.p.value = p.adjust(p.value))

top_slopes <- slopes %>%
  filter(adjusted.p.value<=0.1) %>%
  select(-statistic,-p.value)

# Which words' frequencies have changed the fastest over time?
viz <- words_by_time %>%
  inner_join(top_slopes, by = c("word")) %>%
  ggplot(aes(time_floor,
             count/time_total,
             color = word,
             lty = word)) +
  geom_line(stat = "identity", size = 1.0) +
  # geom_text(aes(label=word)) +
  labs(x = NULL, y = "Word frequency") +
  #scale_x_date(labels = date_format("%m-%Y")) +
  #scale_x_date(date_breaks = "1 month", date_labels =  "%m-%Y") +
  #scale_x_date(date_breaks = "1 month", date_labels =  "%m-%e-%Y") +
  scale_x_date(date_breaks = "1 week", date_labels =  "%b %d") +
  theme(text = element_text(size=12),
        axis.text.x=element_text(angle=60, hjust=1),
        legend.text = element_text(size=rel(1)),
        legend.key.width = unit(1.5, "cm"))
ggplotly(viz)
```


Word Ratios {data-icon="fa-chart-bar"}
==================================================

Row
------------------------------------------------------------
  
### <font size="5">**Word Ratios: Wave v Xfinity**</font>
```{r}
word_ratios <- tidy_tweets %>%
  filter(brand %in% c("Wave","Xfinity")) %>%
  # filter(!str_detect(word, "^@")) %>%
  count(word, brand) %>%
  group_by(word) %>%
  filter(sum(n)>=5) %>%
  ungroup() %>%
  spread(brand, n, fill = 0) %>%
  mutate_if(is.numeric, list(~(. + 1)/(sum(.) + 1))) %>%
  mutate(logratio = log(Wave/Xfinity)) %>%
  arrange(desc(logratio))

att_xfin_word_ratios <- word_ratios %>% 
  arrange(abs(logratio))

wr_1 <- att_xfin_word_ratios %>%
  group_by(logratio < 0) %>%
  top_n(10, abs(logratio)) %>%
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  theme(text = element_text(size=20), legend.position = "none") +
  coord_flip() +
  ylab("log odds ratio (Xfinity/Wave)") +
  scale_fill_discrete(name = "", labels = c("Xfinity", "Wave")) 
ggplotly(wr_1)
```

### <font size="5">**Word Ratios: Wave v CenturyLink**</font>
```{r}
word_ratios <- tidy_tweets %>%
  filter(brand %in% c("Wave","CenturyLink")) %>%
  # filter(!str_detect(word, "^@")) %>%
  count(word, brand) %>%
  group_by(word) %>%
  filter(sum(n)>=5) %>%
  ungroup() %>%
  spread(brand, n, fill = 0) %>%
  mutate_if(is.numeric, list(~(. + 1)/(sum(.) + 1))) %>%
  mutate(logratio = log(Wave/CenturyLink)) %>%
  arrange(desc(logratio))

att_xfin_word_ratios <- word_ratios %>% 
  arrange(abs(logratio))

wr_2 <- att_xfin_word_ratios %>%
  group_by(logratio < 0) %>%
  top_n(10, abs(logratio)) %>%
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  theme(text = element_text(size=20), legend.position = "none") +
  coord_flip() +
  ylab("log odds ratio (CenturyLink/Wave)") +
  scale_fill_discrete(name = "", labels = c("CenturyLink", "Wave")) 
ggplotly(wr_2)
```

### <font size="5">**Word Ratios: Wave v ATT**</font>
```{r}
word_ratios <- tidy_tweets %>%
  filter(brand %in% c("Wave","ATT")) %>%
  # filter(!str_detect(word, "^@")) %>%
  count(word, brand) %>%
  group_by(word) %>%
  filter(sum(n)>=5) %>%
  ungroup() %>%
  spread(brand, n, fill = 0) %>%
  mutate_if(is.numeric, list(~(. + 1)/(sum(.) + 1))) %>%
  mutate(logratio = log(Wave/ATT)) %>%
  arrange(desc(logratio))

att_xfin_word_ratios <- word_ratios %>% 
  arrange(abs(logratio))

wr_3 <- att_xfin_word_ratios %>%
  group_by(logratio < 0) %>%
  top_n(10, abs(logratio)) %>%
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  theme(text = element_text(size=20), legend.position = "none") +
  coord_flip() +
  ylab("log odds ratio (ATT/Wave)") +
  scale_fill_discrete(name = "", labels = c("ATT", "Wave")) 
ggplotly(wr_3)
```

Sentiment Drivers {data-icon="fa-cloud"}
==================================================
  
Row {data-height=450}
--------------------------------------------------

```{r, include=FALSE}
my_lexicon <- afinn_111
```

### <font size="5">**Wave Sentiment Drivers**</font>
```{r}
contributions <- tidy_tweets %>% filter(brand=="Wave") %>%
  inner_join(my_lexicon, by = "word") %>%
  group_by(word) %>%
  summarize(occurences = n(),
            contribution = sum(value))

contributions %>%
  top_n(10, abs(contribution)) %>%
  mutate(word = reorder(word, contribution)) %>%
  ggplot(aes(word, contribution, fill = contribution > 0)) +
  geom_col(show.legend = FALSE) +
  theme(text = element_text(size=16)) +
  coord_flip()
```

### <font size="5">**Xfinity Sentiment Drivers**</font>
```{r}
contributions <- tidy_tweets %>% filter(brand=="Xfinity") %>%
  inner_join(my_lexicon, by = "word") %>%
  group_by(word) %>%
  summarize(occurences = n(),
            contribution = sum(value))

contributions %>%
  top_n(10, abs(contribution)) %>%
  mutate(word = reorder(word, contribution)) %>%
  ggplot(aes(word, contribution, fill = contribution > 0)) +
  geom_col(show.legend = FALSE) +
  theme(text = element_text(size=16)) +
  coord_flip()
```

### <font size="5">**Frontier Sentiment Drivers**</font>
```{r}
contributions <- tidy_tweets %>% filter(brand=="ATT") %>%
  inner_join(my_lexicon, by = "word") %>%
  group_by(word) %>%
  summarize(occurences = n(),
            contribution = sum(value))

contributions %>%
  top_n(10, abs(contribution)) %>%
  mutate(word = reorder(word, contribution)) %>%
  ggplot(aes(word, contribution, fill = contribution > 0)) +
  geom_col(show.legend = FALSE) +
  theme(text = element_text(size=16)) +
  coord_flip()
```

### <font size="5">**CenturyLink Sentiment Drivers**</font>
```{r}
contributions <- tidy_tweets %>% filter(brand=="CenturyLink") %>%
  inner_join(my_lexicon, by = "word") %>%
  group_by(word) %>%
  summarize(occurences = n(),
            contribution = sum(value))

contributions %>%
  top_n(10, abs(contribution)) %>%
  mutate(word = reorder(word, contribution)) %>%
  ggplot(aes(word, contribution, fill = contribution > 0)) +
  geom_col(show.legend = FALSE) +
  theme(text = element_text(size=16)) +
  coord_flip()
```

Row
--------------------------------------------------------
  
```{r, include=FALSE}
my_loughran <- loughran_data
```

### <font size="5">**Wave Sentiment Word Cloud**</font>
```{r}
par(mar=c(.5,1,1,.5))
tidy_tweets %>%
  # filter(date>"2020-01-01") %>%
  filter(brand=="Wave") %>%
  inner_join(my_loughran) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(title.colors=c("green", "orange", "red", "blue", "black"),
                   colors = c("green", "orange", "red", "blue", "black"),
                   title.bg.colors=c("grey90"),
                   max.words = 50,
                   title.size = 3)
par(las=0)
```

### <font size="5">**Xfinity Sentiment Word Cloud**</font>
```{r}
par(mar=c(.5,1,1,.5))
tidy_tweets %>%
  # filter(date>"2020-01-01") %>%
  filter(brand=="Xfinity") %>%
  inner_join(my_loughran) %>%
  count(word, sentiment, sort = TRUE) %>% 
  acast(word ~ sentiment, value.var = "n", fill = 0) %>% 
  comparison.cloud(title.colors=c("green", "orange", "red", "blue", "black"), 
                   colors = c("green", "orange", "red", "blue", "black"),
                   title.bg.colors=c("grey90"),
                   max.words = 50,
                   title.size = 3) 
par(las=0)
```

### <font size="5">**ATT Sentiment Word Cloud**</font>
```{r}
par(mar=c(.5,1,1,.5))
tidy_tweets %>%
  # filter(date>"2020-01-01") %>%
  filter(brand=="ATT") %>%
  inner_join(my_loughran) %>%
  count(word, sentiment, sort = TRUE) %>% 
  acast(word ~ sentiment, value.var = "n", fill = 0) %>% 
  comparison.cloud(title.colors=c("green", "orange", "red", "blue", "black"), 
                   colors = c("green", "orange", "red", "blue", "black"),
                   title.bg.colors=c("grey90"),
                   max.words = 50,
                   title.size = 3) 
par(las=0)
```

### <font size="5">**CenturyLink Sentiment Word Cloud**</font>
```{r}
par(mar=c(.5,1,1,.5))
tidy_tweets %>%
  # filter(date>"2020-01-01") %>%
  filter(brand=="CenturyLink") %>%
  inner_join(my_loughran) %>%
  count(word, sentiment, sort = TRUE) %>% 
  acast(word ~ sentiment, value.var = "n", fill = 0) %>% 
  comparison.cloud(title.colors=c("green", "orange", "red", "blue", "black"), 
                   colors = c("green", "orange", "red", "blue", "black"),
                   title.bg.colors=c("grey90"),
                   max.words = 100,
                   title.size = 3) 
par(las=0)
```

Sentiment Trend {data-icon="fa-smile-beam"}
==================================================
  
Row {data-height=450}
--------------------------------------------------

### <font size="5">**Average Sentiment Score by Day**</font>
```{r}
sentiment_messages <- tidy_tweets %>% 
  filter(brand %in% c("Wave","Xfinity","CenturyLink","ATT")) %>%
  inner_join(my_lexicon, by = "word") %>%
  group_by(created_at, brand) %>%
  summarize(sentiment = mean(value),
            words = n()) %>%
  ungroup() %>%
  filter(words>=5)

p2 <- sentiment_messages %>% 
  group_by(created_at, brand) %>%
  arrange(as.Date(created_at)) %>%
  ggplot(aes(created_at, sentiment, fill = factor(brand), color=brand)) +
  geom_line(show.legend = FALSE) +
  geom_smooth() +
  theme(legend.position = "none", text = element_text(size=12),
        axis.text.x=element_text(angle=60, hjust=1),
        legend.text = element_text(size=rel(1)),
        legend.key.width = unit(1.5, "cm"),
        axis.title.x=element_blank(),
        strip.background = element_rect(fill = "blue"), 
        strip.text = element_text(size = 14)) +
  scale_x_date(date_breaks = "1 weeks") +
  facet_wrap(~ brand, scales = "fixed")
ggplotly(p2, tooltip = c("date","sentiment"), dynamicTicks = TRUE)
```

Word Network {data-icon="fa-connectdevelop"}
==================================================
  
Row
--------------------------------------------------
  
### <font size="5">**Word Network**</font>
```{r, include=FALSE}
# Visualizing nGrams
austen_bigrams_grande <- review_copy %>%
  filter(brand=="Wave") %>%
  unnest_tokens(bigram, review, token = "ngrams", n = 2) 

# Counting and filtering n-grams
austen_bigrams_grande %>% 
  count(bigram, sort = TRUE)

bigrams_separated_grande <- austen_bigrams_grande %>%
  separate(bigram, c("word1", "word2"), sep = " ") 

bigrams_filtered_grande <- bigrams_separated_grande %>% 
  filter(!word1 %in% stop_words$word) %>% 
  filter(!word2 %in% stop_words$word) %>%
  filter(!word1 %in% remove_words) %>%
  filter(!word2 %in% remove_words) %>%
  filter(str_detect(word1, "[a-z]")) %>%
  filter(str_detect(word2, "[a-z]")) 
  
# new bigram counts: 
bigram_counts_grande <- bigrams_filtered_grande %>% 
  count(word1, word2, sort = TRUE)

bigram_graph_grande <- bigram_counts_grande %>% 
  filter(n>10) %>% 
  graph_from_data_frame()
```

```{r}
set.seed(2016) 
par(mar=c(.1,.1,.1,.1))
a <- grid::arrow(type = "closed", 
                 length = unit(.1, "inches")) 
ggraph(bigram_graph_grande, layout = "fr") + 
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour="darkred") + 
  geom_node_point(color = "midnightblue", size = 1.5) + 
  geom_node_text(aes(label = name), vjust = 1, hjust = 1, repel=FALSE, point.padding = unit(0.2, "lines")) + 
  theme_void() 
```

<!-- Google Trends {data-icon="fa fa-google"} -->
<!-- ===================================== -->

<!-- Row -->
<!-- ------------------------------------- -->

<!-- ### <font size="5">**Google Interest Trends by Brand: California**</font> -->

<!-- ```{r} -->
<!-- keywords=c("wave broadband") -->
<!-- country=c('US-CA') -->
<!-- #time=("2019-01-01 2018-08-27") -->
<!-- time='today 12-m' -->
<!-- channel='web' -->
<!-- trends_1 = gtrends(keywords, gprop =channel,geo=country, time = time, onlyInterest = TRUE) -->
<!-- time_trend_1 = trends_1$interest_over_time -->
<!-- # city <- trends$interest_by_city -->

<!-- plot <- ggplot(data=time_trend_1, aes(x=date, y=hits,group=keyword,col=keyword))+ -->
<!--   geom_line()+xlab('Time')+ylab('Relative Interest')+ theme_bw()+ -->
<!--   theme(legend.title = element_blank(),legend.position="bottom",legend.text=element_text(size=12))+ggtitle("Rolling 12-month Google Search Volume - Washington State") -->
<!-- ggplotly(plot) -->
<!-- ``` -->

<!-- ### <font size="5">**Top Related Topics: California**</font> -->

<!-- ```{r} -->
<!-- #keywords_related <- "ziply fiber" -->
<!-- topics_1 = head(gtrends(keywords_1, geo=country_1)$related_topics, n=10) -->
<!-- topics_1$subject <- as.numeric(topics_1$subject) %>% na.omit() -->
<!-- topics_1 <- topics_1 %>% filter(related_topics == "top") -->

<!-- p23 <- ggplot(data=topics_1, aes(x=reorder(value,subject), y=subject, text = paste("Related Topic: ", value, -->
<!--       "<br>Relative Interest: ", subject)))+ -->
<!--  geom_col(fill = "orange", alpha = 0.7) + -->
<!--   xlab('') + -->
<!--   ylab('Relative Interest') + -->
<!--   coord_flip() + -->
<!--   theme(legend.title = element_blank(), -->
<!--         legend.position="bottom", -->
<!--         legend.text=element_text(size=12), -->
<!--         axis.text.x = element_text(size=10,color="darkblue"), -->
<!--         axis.text.y = element_text(size=10,color="darkblue")) + -->
<!--   ylim(0,NA) -->
<!--   # theme_minimal() -->
<!--   # ggtitle("Rolling 12-month Google Search Volume - Washington State") -->
<!-- ggplotly(p23, tooltip = "text") -->
<!-- ``` -->

<!-- Row -->
<!-- ------------------------------------- -->

<!-- ### <font size="5">**Google Interest Trends by Brand: Oregon**</font> -->

<!-- ```{r} -->
<!-- keywords_2=c("wave broadband") -->
<!-- country_2=c('US-OR') -->
<!-- #time=("2019-01-01 2018-08-27") -->
<!-- time='today 12-m' -->
<!-- channel='web' -->
<!-- trends_2 = gtrends(keywords_2, gprop =channel,geo=country_2, time = time, onlyInterest = TRUE) -->
<!-- time_trend_2 = trends_2$interest_over_time -->
<!-- # city <- trends$interest_by_city -->

<!-- plot <- ggplot(data=time_trend_2, aes(x=date, y=hits,group=keyword,col=keyword))+ -->
<!--   geom_line()+xlab('Time')+ylab('Relative Interest')+ theme_bw()+ -->
<!--   theme(legend.title = element_blank(),legend.position="bottom",legend.text=element_text(size=12))+ggtitle("Rolling 12-month Google Search Volume - Washington State") -->
<!-- ggplotly(plot) -->
<!-- ``` -->

<!-- ### <font size="5">**Top Related Topics: Oregon**</font> -->

<!-- ```{r} -->
<!-- #keywords_related <- "ziply fiber" -->
<!-- topics_2 = head(gtrends(keywords_2, geo=country_2)$related_topics, n=10) -->
<!-- topics_2$subject <- as.numeric(topics_2$subject) %>% na.omit() -->
<!-- topics_2 <- topics_2 %>% filter(related_topics == "top") -->

<!-- p23 <- ggplot(data=topics_2, aes(x=reorder(value,subject), y=subject, text = paste("Related Topic: ", value, -->
<!--       "<br>Relative Interest: ", subject)))+ -->
<!--  geom_col(fill = "orange", alpha = 0.7) + -->
<!--   xlab('') + -->
<!--   ylab('Relative Interest') + -->
<!--   coord_flip() + -->
<!--   theme(legend.title = element_blank(), -->
<!--         legend.position="bottom", -->
<!--         legend.text=element_text(size=12), -->
<!--         axis.text.x = element_text(size=10,color="darkblue"), -->
<!--         axis.text.y = element_text(size=10,color="darkblue")) + -->
<!--   ylim(0,NA) -->
<!--   # theme_minimal() -->
<!--   # ggtitle("Rolling 12-month Google Search Volume - Washington State") -->
<!-- ggplotly(p23, tooltip = "text") -->
<!-- ``` -->

Recent Reviews {data-icon="far fa-comments"}
==================================================

```{r, include=FALSE}
sentiment_messages_polarity <- tidy_tweets %>%
  # filter(date>=as.Date("2020-01-01")) %>%
  # filter(src != "FaceBook") %>%
  inner_join(my_lexicon, by = "word") %>%
  group_by(text, brand, created_at, src, region, location) %>%
  summarize(sentiment = sum(value),
            words = n()) %>%
  ungroup() %>%
  #filter(words>= 4) %>%
  mutate(polarity = ifelse(sentiment>=4,"Very Positive",ifelse(sentiment>=1 & sentiment<4, "Positive", ifelse(sentiment<=(-1) & sentiment>=(-3), "Negative", ifelse(sentiment<(-3),"Very Negative","Neutral")))))

#Very Negative (rating -5 or -4)
#Negative (rating -3, -2, or -1)
#Positive (rating 1, 2, or 3)
#Very Positive (rating 4 or 5)
```

Row
--------------------------------------------------

### <font size="5">**Recent Social Media Reviews and Sentiment Polarity**</font>
```{r}
DT::datatable(sentiment_messages_polarity[,-c(7,8)],
          # caption = "REVIEWS",
          rownames = TRUE,
          colnames = c(
            "BRAND" = "brand",
            "REGION" = "region",
            "LOCATION" = "location",
            "DATE" = "created_at",
            "REVIEW" = "text",
            "SENTIMENT" = "polarity",
            "SOURCE" = "src"
          ),
          filter = "top",
          options = list(pageLength=25))
```