---
title: "TEXT DATA ANALYTICS"
author:  "Chris Bailey"
output: 
  flexdashboard::flex_dashboard:
    theme: cosmo
    orientation: rows
    vertical_layout: fill
runtime: shiny
resource:
  - raw_text_consolidated.csv
  - loughran.csv
  - afinn_111.xlsx
---

```{r}
library(flexdashboard)
library(shiny)
library(shinythemes)
library(openintro)
library(highcharter)
library(knitr)
library(lubridate) 
library(scales) 
library(tidytext) 
library(tidyverse)
library(broom) 
library(textdata)
library(plotly)
library(wordcloud)
library(RColorBrewer)
library(reshape2) 
library(ggraph)
library(igraph)
library(plotly)
library(gtrendsR)
library(reshape2)
library(ggrepel)
library(grid)
library(crosstalk)
library(htmltools)
library(htmlwidgets)
library(htmltools)
library(DT)

theme_set(theme_light())
mycolors <- c("blue", "#FFC125", "darkgreen", "darkorange")

review <- readr::read_csv('raw_text_consolidated.csv',
                          col_names = TRUE,
                          na = c("", "NA"),
                          trim_ws = TRUE,
                          skip = 0,
                          progress = show_progress(), 
                          skip_empty_rows = TRUE) %>%
  filter_at(vars(rec,created_at,review,src,brand,region,location,market),all_vars(!is.na(.))) %>%
  mutate(week = as.Date(floor_date(created_at, "week", week_start = 1))) %>%
  filter(!brand %in% c('Consolidated','Frontier','SonicNet','Spectrum')) 

review$created_at <- as.Date(review$created_at)

review <- review %>% filter(created_at>="2021-01-01")

maxdt <- max(review$created_at)
loughran_data <- readr::read_csv('loughran.csv')
afinn_111 <- readxl::read_xlsx('afinn_111.xlsx')
my_loughran <- loughran_data %>% filter(sentiment %in% c("positive","negative","constraining","litigious"))
my_lexicon <- afinn_111

review_copy <- review 

review_copy$review <-  gsub("https\\S*", "", review_copy$review)
review_copy$review <-  gsub("@\\S*", "", review_copy$review)
review_copy$review <-  gsub("amp", "", review_copy$review)
review_copy$review <-  gsub("[\r\n]", "", review_copy$review)
review_copy$review <-  gsub("[[:punct:]]", "", review_copy$review)
replace_reg1 <- "https://t.co/[A-Za-z\\d]+|" 
replace_reg2 <- "http://[A-Za-z\\d]+|&amp;|&lt;|&gt;|RT|https+|" 
replace_reg <- paste0(replace_reg1, replace_reg2) 
unnest_reg <- "([^A-Za-z_\\d#@']|'(?![A-Za-z_\\d#@]))"
remove_words <- c("hey",
                  "u001f620",
                  "comcast",
                  "xfinity",
                  "wave",
                  "att",
                  "centurylink",
                  "ziply",
                  "frontier",
                  "century",
                  "link",
                  "amongus",
                  "apparently"
                  )

tidy_tweets <- review_copy %>%
  # filter(!str_detect(text, "^RT")) %>%
  mutate(text = str_replace_all(review, replace_reg, "")) %>% 
  # unnest_tokens(word, text, token = "tweets", strip_punct =TRUE) %>%
  unnest_tokens(word, review, token = "regex", pattern = unnest_reg) %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         !word %in% remove_words,
         str_detect(word, "[a-z]"))

tidy_tweets_copy <- tidy_tweets 
# %>%
#   filter(market %in% c('Wave North','Wave South'))

sd <- SharedData$new(review_copy)
sd1 <- SharedData$new(tidy_tweets)
sd2 <- SharedData$new(review_copy)
sd3 <- SharedData$new(tidy_tweets)
sd4 <- SharedData$new(tidy_tweets_copy)
```

Data {data-icon="fa-database"}
==================================================

Inputs {.sidebar}
--------------------------------------------------

### <font size="5">**Filters**</font>

```{r}
bscols(widths = c(10,NA,NA),
  list(
    filter_select("market", "Select Market:", sd, ~market, allLevels = FALSE),
    filter_select("brand", " Select Brand:", sd, ~brand, allLevels = FALSE),
    filter_select("period", "Select Week(s):", sd, ~week, allLevels = FALSE),
    filter_select("source", "Select Source:", sd, ~src, allLevels = FALSE)
    )
  )
```

#### <font size="3">**Date Last Refreshed:**</font>
#### <font size="3">**```r maxdt```**</font>


Row {data-height=350}
--------------------------------------------------

### <font size="5">**Count of Reviews**</font> {.value-box data-width=150}

```{r}
renderValueBox({
  
  total_reviews <- sd$data(withSelection = TRUE, withFilter = TRUE) %>%
    group_by(market) %>%
    summarise(units = length(unique(rec))) 
  
  value <- sum(total_reviews$units)

  if(!is.infinite(value) && !is.nan(value) && !is.na(value)) { 
  if(value >=1){
    valueBox(value = format(value, nsmall=0, big.mark = ","), icon = "far fa-comments", color = "primary")
    } else {
valueBox(value = "No records to display", icon = "fas fa-comments", color = "warning")
    }
  }

})
```

### <font size="5">**Social Media Reviews by Market**</font>

```{r}
renderPlotly({

  brand_cnt <- sd$data(withSelection = TRUE, withFilter = TRUE) %>%
    group_by(market) %>%
    summarise(units = length(unique(rec))) %>%
    arrange(desc(units))

  p1 <- brand_cnt %>%
    plot_ly(labels = ~market,
            values = ~units,
            marker = list(colors = mycolors)) %>%
    add_pie(hole = 0.4) %>%
    layout(xaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F),
         yaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F))
  ggplotly(p1)
})
```

### <font size="5">**Social Media Reviews by Brand**</font>

```{r}
renderPlotly({

  brand_cnt <- sd$data(withSelection = TRUE, withFilter = TRUE) %>%
    group_by(brand) %>%
    summarise(units = length(unique(rec))) %>%
    arrange(desc(units))

  p1 <- brand_cnt %>%
    plot_ly(labels = ~brand,
            values = ~units,
            marker = list(colors = mycolors)) %>%
    add_pie(hole = 0.4) %>%
    layout(xaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F),
         yaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F))
  ggplotly(p1)
})
```

### <font size="5">**Social Media Reviews by Location**</font>

```{r}
renderPlotly({

  location_cnt <- sd$data(withSelection = TRUE, withFilter = TRUE) %>%
    group_by(location) %>%
    summarise(units = length(unique(rec))) %>%
    arrange(desc(units)) %>%
    head()

  p2 <- location_cnt %>%
    plot_ly(labels = ~location,
            values = ~units,
            marker = list(colors = mycolors)) %>%
    add_pie(hole = 0.4) %>%
    layout(xaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F),
         yaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F))
  ggplotly(p2)
})
```

Row
--------------------------------------------------

### <font size="5">**Social Media Reviews by Brand**</font>
```{r}
renderPlot({

  review_ts_chart <- sd$data(withSelection = TRUE, withFilter = TRUE) %>%
    # select(rec,created_at, review, week, brand, region, src, market) %>%
    arrange(brand, as.Date(created_at))

  review_ts_chart %>%
    group_by(brand, created_at) %>%
    summarize(count = length(unique(rec))) %>%
    arrange(brand, as.Date(created_at)) %>%
    ggplot(aes(created_at, count, brand, fill = factor(brand), color=brand)) +
    geom_point(size = 3) +
    geom_line(size = 1) +
    geom_area(alpha = 0.2) +
    facet_wrap(~brand) +
    expand_limits(y=0) +
    #scale_y_continuous(limits = c(0,100)) +
    labs(title = "Count of Reviews by Brand",
            y = "Review count",
            x = "Date",
         subtitle = "Includes reviews sourced from FaceBook, Twitter & Yelp") +
    theme(strip.background = element_rect(fill = "blue"),
          strip.text = element_text(size = 16, face = "bold"),
          legend.position = "none",
          plot.title.position = "plot",
          axis.text.x = element_text(size = 12, angle=90, hjust=1)) +
    scale_x_date(date_breaks = "1 week", date_labels =  "%b %d")
    # scale_x_date(labels = date_format("%m-%Y"))
})
```

Topics {data-icon="fa-chart-line"}
==================================================

Sidebar {.sidebar}
--------------------------------------------------

### <font size="5">**Filters**</font>

```{r}
# f2 <- filter_select("market", "Select Market:", sd1, ~market, allLevels = FALSE)
f3 <- filter_select("brand", "Select Brand:", sd1, ~brand, allLevels = FALSE)

filter_2 <- bscols(
  list(f3)
  )

filter_2
```

Row
--------------------------------------------------

### <font size="5">**Key Topics**</font>
```{r}
renderPlot({
  
  top_word <- sd1$data(withSelection = TRUE, withFilter = TRUE) %>%
  count(word, week) %>%
  bind_tf_idf(word, week, n) %>%
  arrange(desc(tf_idf)) %>%
  group_by(week) %>%
  #top_n(1, tf_idf) %>%
  distinct(week, .keep_all = TRUE) %>%
  arrange(week)

  shiny::validate(
    shiny::need(nrow(top_word) != 0,
         "Oh snap!  No results due to insufficient data.")
  )
  top_word

top_word %>%
  ggplot(aes(week, n, label= word, color=word)) +
  geom_line(color = "royalblue", size = 2) +
  geom_point(color = "royalblue", size = 5) +
  # geom_text_repel(aes(label = word, color = word)) +
  geom_label_repel(size = 8,
                   box.padding = unit(0.5, "lines")) +
  expand_limits(y = 0) +
  labs(
          title = "Represents the number of reviews that contain the key words shown in the graph.",
          y = "Word count",
          x = "Date") +
  theme(legend.position = "none",
        plot.title=element_text(size=18),
        # axis.text=element_text(size=16),
        axis.title=element_text(size=18),
        axis.text.x = element_text(size = 18, angle=90, hjust=1),
        axis.text.y = element_text(size = 18)
        ) +
    scale_x_date(date_breaks = "1 week", date_labels =  "%b %d")
})
```

Row
--------------------------------------------------

### <font size="5">**Trending Words**</font>
```{r}
renderPlotly({
# rolling_dt <- today() - months(3) #lubridate

words_by_time <- sd1$data(withSelection = TRUE, withFilter = TRUE) %>%
  # filter(brand=="Wave") %>%
  # filter(!str_detect(word, "^@")) %>%
  # filter(date> "2020-01-01") %>%
  mutate(time_floor = floor_date(created_at, unit = "week")) %>%
  count(time_floor, word) %>%
  # count(time_floor, period, word) %>%
  ungroup() %>%
  group_by(time_floor) %>%
  # group_by(period, time_floor) %>%
  mutate(time_total = sum(n)) %>%
  group_by(word) %>%
  mutate(word_total = sum(n)) %>%
  ungroup() %>%
  rename(count = n) %>%
  filter(word_total>=20)  # nbr of words used at least x times

shiny::validate(
    shiny::need(nrow(words_by_time) != 0,
         "Oh snap!  No results due to insufficient data.")
  )
  words_by_time

nested_data <- words_by_time %>%
  # nest(-word,-time_floor)
  nest_legacy(-word)

shiny::validate(
    shiny::need(nrow(nested_data) != 0,
         "Oh snap!  No results due to insufficient data.")
  )
  nested_data

nested_models <- nested_data %>%
  mutate(models = map(data, ~glm(cbind(count, time_total) ~ time_floor, ., family = "binomial")))

shiny::validate(
    shiny::need(nrow(nested_models) != 0,
         "Oh snap!  No results due to insufficient data.")
  )
  nested_models

slopes <- nested_models %>%
  unnest_legacy(map(models, tidy)) %>%
  filter(term == "time_floor") %>%
  mutate(adjusted.p.value = p.adjust(p.value))

top_slopes <- slopes %>%
  filter(adjusted.p.value<=0.05) %>%
  select(-statistic,-p.value)

shiny::validate(
    shiny::need(nrow(top_slopes) != 0,
         "Oh snap!  No results due to insufficient data.")
  )
  top_slopes

# Which words' frequencies have changed the fastest over time?
viz <- words_by_time %>%
  inner_join(top_slopes, by = c("word")) %>%
  ggplot(aes(time_floor,
             count/time_total,
             color = word,
             lty = word)) +
  geom_line(stat = "identity", size = 1.0) +
  # geom_text(aes(label=word)) +
  labs(x = NULL, y = "Word frequency") +
  labs(title = "Key words exhibiting significant frequency changes over time.",
          y = "Word count",
          x = "Date") +
  #scale_x_date(labels = date_format("%m-%Y")) +
  #scale_x_date(date_breaks = "1 month", date_labels =  "%m-%Y") +
  #scale_x_date(date_breaks = "1 month", date_labels =  "%m-%e-%Y") +
  scale_x_date(date_breaks = "1 week", date_labels =  "%b %d") +
  theme(text = element_text(size=12),
        axis.text.x=element_text(size=12,angle=90, hjust=1),
        legend.text = element_text(size=rel(1)),
        legend.key.width = unit(1.5, "cm"),
        axis.text.y = element_text(size = 16)
        )
ggplotly(viz)
})
```

Word Ratios {data-icon="fa-chart-bar"}
==================================================

Sidebar {.sidebar}
--------------------------------------------------

### <font size="5">**Filters**</font>

```{r}
f85 <- filter_select("market", "Select Market:", sd4, ~market, allLevels = FALSE)
# f118 <- filter_select("period", "Select Week(s):", sd4, ~week, allLevels = FALSE)

filter_6 <- bscols(
  list(f85)
  )

filter_6
```

Row
------------------------------------------------------------

### <font size="5">**Word Ratios: Wave v Xfinity**</font>
```{r}
renderPlotly({
word_ratios <- sd4$data(withSelection = TRUE, withFilter = TRUE) %>%
  filter(market %in% c("Wave North","Wave South")) %>%
  filter(brand %in% c("Wave","Xfinity")) %>%
  # filter(!str_detect(word, "^@")) %>%
  count(word, brand) %>%
  group_by(word) %>%
  filter(sum(n)>=5) %>%
  ungroup() %>%
  spread(brand, n, fill = 0) %>%
  mutate_if(is.numeric, list(~(. + 1)/(sum(.) + 1))) %>%
  mutate(logratio = log(Wave/Xfinity)) %>%
  arrange(desc(logratio))

xfin_word_ratios <- word_ratios %>%
  arrange(abs(logratio))

wr_1 <- xfin_word_ratios %>%
  group_by(logratio < 0) %>%
  top_n(10, abs(logratio)) %>%
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  theme(text = element_text(size=16), legend.position = "none") +
  coord_flip() +
  ylab("<-Xfinity/Wave->") +
  scale_fill_discrete(name = "", labels = c("Xfinity", "Wave"))
ggplotly(wr_1)
})
```

### <font size="5">**Word Ratios: Wave v CenturyLink**</font>
```{r}
renderPlotly({
word_ratios <- sd4$data(withSelection = TRUE, withFilter = TRUE) %>%
  filter(market %in% c("Wave North","Wave South")) %>%
  filter(brand %in% c("Wave","CenturyLink")) %>%
  # filter(!str_detect(word, "^@")) %>%
  count(word, brand) %>%
  group_by(word) %>%
  filter(sum(n)>=5) %>%
  ungroup() %>%
  spread(brand, n, fill = 0) %>%
  mutate_if(is.numeric, list(~(. + 1)/(sum(.) + 1))) %>%
  mutate(logratio = log(Wave/CenturyLink)) %>%
  arrange(desc(logratio))

clink_word_ratios <- word_ratios %>%
  arrange(abs(logratio))

wr_2 <-clink_word_ratios %>%
  group_by(logratio < 0) %>%
  top_n(10, abs(logratio)) %>%
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  theme(text = element_text(size=16), legend.position = "none") +
  coord_flip() +
  ylab("<-CenturyLink/Wave->") +
  scale_fill_discrete(name = "", labels = c("CenturyLink", "Wave"))
ggplotly(wr_2)
})
```

### <font size="5">**Word Ratios: Wave v ATT**</font>
```{r}
renderPlotly({
word_ratios <- sd4$data(withSelection = TRUE, withFilter = TRUE) %>%
  filter(market %in% c("Wave North","Wave South")) %>%
  filter(brand %in% c("Wave","ATT")) %>%
  # filter(!str_detect(word, "^@")) %>%
  count(word, brand) %>%
  group_by(word) %>%
  filter(sum(n)>=5) %>%
  ungroup() %>%
  spread(brand, n, fill = 0) %>%
  mutate_if(is.numeric, list(~(. + 1)/(sum(.) + 1))) %>%
  mutate(logratio = log(Wave/ATT)) %>%
  arrange(desc(logratio))

att_word_ratios <- word_ratios %>%
  arrange(abs(logratio))

wr_3 <- att_word_ratios %>%
  group_by(logratio < 0) %>%
  top_n(10, abs(logratio)) %>%
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  theme(text = element_text(size=16), legend.position = "none") +
  coord_flip() +
  ylab("<-ATT/Wave->") +
  scale_fill_discrete(name = "", labels = c("ATT", "Wave"))
ggplotly(wr_3)
})
```

### <font size="5">**Word Ratios: Wave v Ziply**</font>
```{r}
renderPlotly({
word_ratios <- sd4$data(withSelection = TRUE, withFilter = TRUE) %>%
  filter(market %in% c("Wave North","Wave South")) %>%
  filter(brand %in% c("Wave","Ziply")) %>%
  # filter(!str_detect(word, "^@")) %>%
  count(word, brand) %>%
  group_by(word) %>%
  filter(sum(n)>=5) %>%
  ungroup() %>%
  spread(brand, n, fill = 0) %>%
  mutate_if(is.numeric, list(~(. + 1)/(sum(.) + 1))) %>%
  mutate(logratio = log(Wave/Ziply)) %>%
  arrange(desc(logratio))

ziply_word_ratios <- word_ratios %>%
  arrange(abs(logratio))

wr_4 <- ziply_word_ratios %>%
  group_by(logratio < 0) %>%
  top_n(10, abs(logratio)) %>%
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  theme(text = element_text(size=16), legend.position = "none") +
  coord_flip() +
  ylab("<-Ziply/Wave->") +
  scale_fill_discrete(name = "", labels = c("Ziply", "Wave"))
ggplotly(wr_4)
})
```

Sentiment Driver Word Cloud {data-icon="fas fa-cloud"}
==================================================

Sidebar {.sidebar}
--------------------------------------------------

### <font size="5">**Filters**</font>

```{r}
f35 <- filter_select("market", "Select Market:", sd3, ~market, allLevels = FALSE)
f5 <- filter_select("brand", "Select Brand:", sd3, ~brand, allLevels = FALSE)
f115 <- filter_select("period", "Select Week(s):", sd3, ~week, allLevels = FALSE)

filter_3 <- bscols(
  list(f35,f5,f115)
  )

filter_3
```

Row {data-height=450}
--------------------------------------------------

### <font size="5">**Sentiment Drivers**</font>
```{r}
renderPlot({

contributions <- sd3$data(withSelection = TRUE, withFilter = TRUE) %>%
  inner_join(my_lexicon, by = "word") %>%
  group_by(word) %>%
  summarize(occurences = n(),
            contribution = sum(value))

shiny::validate(
    shiny::need(nrow(contributions) != 0,
         "Oh snap!  No results due to insufficient data.")
  )
  contributions


contributions %>%
  top_n(16, abs(contribution)) %>%
  mutate(word = reorder(word, contribution)) %>%
  ggplot(aes(word, contribution, fill = contribution > 0)) +
  geom_col(show.legend = FALSE) +
  theme(text = element_text(size=20)) +
  coord_flip()
})
```

### <font size="5">**Sentiment Driver Word Cloud**</font>
```{r}
renderPlot({
  cloud_plot <- sd3$data(withSelection = TRUE, withFilter = TRUE) 
    
  par(mar=c(.5,.5,.5,.5))
  
  cloud_plot %>%
  inner_join(my_loughran) %>%
  count(word, sentiment, sort = TRUE) %>%
  mutate(sentiment = toupper(sentiment)) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(title.colors=c("black","blue","red","green"),
                   colors = c("black","blue","red","green"),
                   title.bg.colors=c("grey90"),
                   max.words = 250,
                   title.size = 3,
                   scale=c(7,1))
  # comparison.cloud(title.colors=c("green", "orange", "red", "blue", "black"),
  #                  colors = c("green", "orange", "red", "blue", "black"),
  #                  title.bg.colors=c("grey90"),
  #                  max.words = 250,
  #                  title.size = 3,
  #                  scale=c(7,1))
  # par(las=0)
})
```

Sentiment Trend {data-icon="fa-smile-beam"}
==================================================

Row {data-height=450}
--------------------------------------------------

### <font size="5">**Average Sentiment Score by Day**</font>
```{r}

sentiment_messages <- tidy_tweets %>%
  filter(brand %in% c("Wave","Xfinity","CenturyLink","ATT","Ziply")) %>%
  inner_join(my_lexicon, by = "word") %>%
  group_by(created_at, brand) %>%
  summarize(sentiment = mean(value),
            words = n()) %>%
  ungroup() %>%
  filter(words>=2)

p2 <- sentiment_messages %>%
  group_by(created_at, brand) %>%
  arrange(brand,as.Date(created_at)) %>%
  ggplot(aes(created_at, sentiment, fill = sentiment>0, rm.na = TRUE)) +
  geom_col(alpha = 0.7, na.rm = TRUE) +
 # geom_area(na.rm = TRUE, alpha = 0.3, outline.type = "both") +
  # scale_colour_manual(name = 'Sentiment > 0', values = setNames(c('green','red'),c(T, F))) +
  # geom_line(show.legend = FALSE) +
  theme(legend.position = "none", text = element_text(size=12),
        axis.text.x=element_text(angle=0, hjust=1),
        legend.text = element_text(size=rel(1)),
        legend.key.width = unit(1.5, "cm"),
        axis.title.x=element_blank(),
        strip.background = element_rect(fill = "blue"),
        strip.text = element_text(size = 14)) +
  scale_x_date(labels = function(x) format(x, "%d-%b")) +
  facet_wrap(~brand, scales = "free")
ggplotly(p2, tooltip = c("date","sentiment"), dynamicTicks = TRUE)

```

Word Network {data-icon="fa-connectdevelop"}
==================================================

Sidebar {.sidebar}
--------------------------------------------------

### <font size="5">**Filters**</font>

```{r}
f15 <- filter_select("brand", "Select Brand:", sd2, ~brand, allLevels = FALSE)
f55 <- filter_select("market", "Select Market:", sd2, ~market, allLevels = FALSE)
# f120 <- filter_select("period", "Select Week(s):", sd2, ~week, allLevels = FALSE)

filter_4 <- bscols(
  list(f55,f15)
  )

filter_4
```

Row
--------------------------------------------------

### <font size="5">**Word Network**</font>
```{r}
renderPlot({

  bigrams <- sd2$data(withSelection = TRUE, withFilter = TRUE) %>%
    filter(!brand %in% c("Consolidated","SonicNet","Ziply")) %>%
  unnest_tokens(bigram, review, token = "ngrams", n = 2)

bigrams %>%
  count(bigram, sort = TRUE)

bigrams_separated <- bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(!word1 %in% remove_words) %>%
  filter(!word2 %in% remove_words) %>%
  filter(str_detect(word1, "[a-z]")) %>%
  filter(str_detect(word2, "[a-z]"))

# new bigram counts:
bigram_counts <- bigrams_filtered %>%
  count(word1, word2, sort = TRUE)

bigram_graph <- bigram_counts %>%
  filter(n>=5) %>%
  graph_from_data_frame()

set.seed(2016)
par(mar=c(.1,.1,.1,.1))
a <- grid::arrow(type = "open",
                 length = unit(.03, "inches"),
                 ends = "last")
ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour="blue") +
  geom_node_point(color = "blue", size = 6) +
  geom_node_text(aes(label = name), size=6, vjust = 1, hjust = 1, repel=FALSE, point.padding = unit(0.2, "lines"))
})
```

Recent Reviews {data-icon="far fa-comments"}
==================================================

### <font size="5">**Recent Social Media Reviews and Sentiment Polarity**</font>

```{r}
renderDT({
  
  sentiment_messages_polarity <- tidy_tweets %>%
  # filter(date>=as.Date("2020-01-01")) %>%
  # filter(src != "FaceBook") %>%
  inner_join(my_lexicon, by = "word") %>%
  group_by(text, brand, created_at, src, region, location) %>%
  summarize(sentiment = sum(value),
            words = n()) %>%
  ungroup() %>%
  # filter(words>= 4) %>%
  mutate(polarity = ifelse(sentiment>=6,"Very Positive",ifelse(sentiment>=4 & sentiment<6, "Positive", ifelse(sentiment<=(-1) & sentiment>=(-3), "Negative", ifelse(sentiment<(-3),"Very Negative","Neutral")))))

#Very Negative (rating -5 or -4)
#Negative (rating -3, -2, or -1)
#Positive (rating 1, 2, or 3)
#Very Positive (rating 4 or 5)

DT::datatable(sentiment_messages_polarity[,-c(7,8)],
          # caption = "REVIEWS",
          rownames = TRUE,
          colnames = c(
            "BRAND" = "brand",
            "REGION" = "region",
            "LOCATION" = "location",
            "DATE" = "created_at",
            "REVIEW" = "text",
            "SENTIMENT" = "polarity",
            "SOURCE" = "src"
          ),
          filter = "top",
          options = list(
            pageLength=25, 
            scrollY = '800px',
            pageLength = 1000,
            autoWidth=TRUE))

})
```




<!-- # f1 <- filter_select("market", "Select Market:", sd, ~market, allLevels = FALSE) -->
<!-- # f11 <- filter_select("brand", " Select Brand:", sd, ~brand, allLevels = FALSE) -->
<!-- # f111 <- filter_select("period", "Select Week(s):", sd, ~week, allLevels = FALSE) -->
<!-- # f1111 <- filter_select("source", "Select Source:", sd, ~src, allLevels = FALSE) -->
<!-- #  -->
<!-- # filter_1 <- bscols(widths = c(NA,NA,NA), -->
<!-- #   list(f1,f11,f111,f1111) -->
<!-- #   ) -->
<!-- #  -->
<!-- # filter_1 -->


<!-- # div( -->
<!-- #   div(class = "title", -->
<!-- #       h2("2019 NFL Team Stats & Ratings")), -->
<!-- #   class = "filtertext", -->
<!-- #   bscols( -->
<!-- #     widths = c(3, NA), -->
<!-- #     list( -->
<!-- #       f1,f11,f111,f1111 -->
<!-- #     ) -->
<!-- #   ), -->
<!-- #   div(class = "linebreak") -->
<!-- # ) -->